Your Paper Title

### 2025-03-28 paper/paper.qmd
changed how I wrote my reference so it actually use the reference.bib

    The relationship between temperature and the flowering phenology of cherry blossoms (Prunus species, more commonly known as sakura) represents a unique merge of cultural heritage and biological science. For centuries, the timing of the sakura blooming has held profound cultural significance throughout East Asia, particularly in Japan, where the tradition of hanami (flower viewing) dates back to the Heian period. Beyond its cultural importance, the flowering phenology of sakura serves as a sensitive bioindicator of climate variability and change, with extensive historical records providing an exceptional opportunity to examine long-term temperature-phenology relationships (Aono & Kazui, 2008).

    This review examines the extensive body of literature addressing the correlation between temperature and sakura flowering dates, integrating perspectives from plant biology, phenological modeling, climatology, and cultural studies. The biological mechanisms underlying temperature sensitivity in cherry blossoms involve complex interactions between winter chilling requirements and early spring temperatures (Allen et al., 2014). Concurrently, the cultural documentation of flowering dates through imperial court diaries, temple records, and festival calendars has created one of the longest continuous biological datasets in existence, with some records from Kyoto extending back to 812 CE (Aono & Kazui, 2008).

    To begin with, Acevedo's thesis, "Sakura Storytellers" provides a rich cultural context for understanding cherry blossom phenology in Kyoto (2023). Her research highlights the 1200-year flowering record of Prunus jamasakura in Kyoto, describing it as "the longest and most complete phenological record in existence." These records, compiled from imperial court documents, poetry, and newspaper accounts of hanami celebrations, reveal that Kyoto's cherry trees have responded to major climate fluctuations throughout history, with progressive advancement in bloom dates occurring after approximately 1830. According to Aono and Kazui's analysis referenced in the thesis, cherry trees in Kyoto are currently experiencing warmer conditions than at any time in the past twelve centuries, resulting in average flowering dates that are seven days earlier in the 1971-2000 period compared to historical averages (2008). Beyond scientific significance, Acevedo explores how sakura in Kyoto have traditionally served as indicators of agricultural prosperity, with early-falling petals considered inauspicious for rice harvests, demonstrating their enduring role as both cultural and climatic storytellers in Japanese society.

    Next, Xu et al.'s research provides significant physiological evidence supporting the temperature-flowering relationship in cherry trees (2023). Their study not only documented how temperature fluctuations caused 2-3 day shifts in flowering periods between 2016-2017, but also established varying cold tolerance rankings among cherry varieties that influence bloom timing. The authors revealed the underlying hormonal mechanisms—specifically changes in ABA, ZR, IAA, and GA3 levels—that regulate flower bud differentiation in response to temperature changes. This work strengthens our understanding of how temperature directly affects cherry blossom phenology through specific physiological pathways, offering valuable context for examining historical sakura flowering records in Kyoto and predicting how future climate patterns might alter traditional bloom timing.

    In addition, Allen et al.'s research, "Modeling daily flowering probabilities" offers rigorous quantitative predictions about cherry blossom phenology under climate change in Japan (2014). They analyzed four cherry taxa (Prunus spachiana, P. × yedoensis, P. jamasakura, and P. lannesiana) using flexible Bayesian survival regression models applied to a 29-year dataset from Tama Forest Cherry Preservation Garden in Hachioji. Their approach incorporated both chilling requirements and heat accumulation mechanisms, finding that early-flowering species like P. spachiana were particularly sensitive to warming temperatures. The models predicted that all studied cherry taxa will flower approximately 30 days earlier by 2100 under the A1B emissions scenario, with 2-6 days greater uncertainty around mean flowering dates. The researchers find that sequential models (where trees require chilling before responding to warming) better predicted flowering times than simpler approaches. The study demonstrates that while cherry trees will continue to meet their chilling requirements under projected climate scenarios, accelerated heat accumulation will drive the dramatic advancement in flowering times

>>>>

    The relationship between temperature and the flowering phenology of cherry blossoms (Prunus species, more commonly known as sakura) represents a unique merge of cultural heritage and biological science. For centuries, the timing of the sakura blooming has held profound cultural significance throughout East Asia, particularly in Japan, where the tradition of hanami (flower viewing) dates back to the Heian period. Beyond its cultural importance, the flowering phenology of sakura serves as a sensitive bioindicator of climate variability and change, with extensive historical records providing an exceptional opportunity to examine long-term temperature-phenology relationships [@Aono2008].

    This review examines the extensive body of literature addressing the correlation between temperature and sakura flowering dates, integrating perspectives from plant biology, phenological modeling, climatology, and cultural studies. The biological mechanisms underlying temperature sensitivity in cherry blossoms involve complex interactions between winter chilling requirements and early spring temperatures (Allen et al., 2014). Concurrently, the cultural documentation of flowering dates through imperial court diaries, temple records, and festival calendars has created one of the longest continuous biological datasets in existence, with some records from Kyoto extending back to 812 CE [@Aono2008].

    To begin with, Acevedo's thesis, "Sakura Storytellers" provides a rich cultural context for understanding cherry blossom phenology in Kyoto [@Acevedo2023]. Her research highlights the 1200-year flowering record of Prunus jamasakura in Kyoto, describing it as "the longest and most complete phenological record in existence." These records, compiled from imperial court documents, poetry, and newspaper accounts of hanami celebrations, reveal that Kyoto's cherry trees have responded to major climate fluctuations throughout history, with progressive advancement in bloom dates occurring after approximately 1830. According to Aono and Kazui's analysis referenced in the thesis, cherry trees in Kyoto are currently experiencing warmer conditions than at any time in the past twelve centuries, resulting in average flowering dates that are seven days earlier in the 1971-2000 period compared to historical averages [@Aono2008]. Beyond scientific significance, Acevedo explores how sakura in Kyoto have traditionally served as indicators of agricultural prosperity, with early-falling petals considered inauspicious for rice harvests, demonstrating their enduring role as both cultural and climatic storytellers in Japanese society.

    Next, Xu et al.'s research provides significant physiological evidence supporting the temperature-flowering relationship in cherry trees [@Xu2023]. Their study not only documented how temperature fluctuations caused 2-3 day shifts in flowering periods between 2016-2017, but also established varying cold tolerance rankings among cherry varieties that influence bloom timing. The authors revealed the underlying hormonal mechanisms—specifically changes in ABA, ZR, IAA, and GA3 levels—that regulate flower bud differentiation in response to temperature changes. This work strengthens our understanding of how temperature directly affects cherry blossom phenology through specific physiological pathways, offering valuable context for examining historical sakura flowering records in Kyoto and predicting how future climate patterns might alter traditional bloom timing.

    In addition, Allen et al.'s research, "Modeling daily flowering probabilities" offers rigorous quantitative predictions about cherry blossom phenology under climate change in Japan [@Allen2014]. They analyzed four cherry taxa (Prunus spachiana, P. × yedoensis, P. jamasakura, and P. lannesiana) using flexible Bayesian survival regression models applied to a 29-year dataset from Tama Forest Cherry Preservation Garden in Hachioji. Their approach incorporated both chilling requirements and heat accumulation mechanisms, finding that early-flowering species like P. spachiana were particularly sensitive to warming temperatures. The models predicted that all studied cherry taxa will flower approximately 30 days earlier by 2100 under the A1B emissions scenario, with 2-6 days greater uncertainty around mean flowering dates. The researchers find that sequential models (where trees require chilling before responding to warming) better predicted flowering times than simpler approaches. The study demonstrates that while cherry trees will continue to meet their chilling requirements under projected climate scenarios, accelerated heat accumulation will drive the dramatic advancement in flowering times.
